Final Project

### 2025-04-30 MSSC5750_Project.qmd
LDA

plot(explainer, plot_phi0 = FALSE, index_x_explain = 1)

shapObj <-shapviz(explainer)
sv_importance(shapObj, kind="beeswarm", show_numbers = TRUE, max_display=15)

>>>>

plot(explainer, plot_phi0 = FALSE, index_x_explain = 1)
####
shapObj <-shapviz(explainer)
sv_importance(shapObj, kind="beeswarm", show_numbers = TRUE, max_display=15)
